module2_eco_pol_factors

### 2022-02-26 moduletwoanalysis.Rmd
more graphs on risk and benefit

```
```{r}
levels(module2)
```

```{r}
%>%
  spread(Perceived_Risk, n)%>%
  select("Technology", "Extremely risky", "Very risky", "Moderately risky", "Slightly risky", "Not at all risky", "Rather not say/Don't know")
```

@@

@@

>>>>

@@

# fix ugly visual. Rearrange from extremely risky to not at all risky. Red to green, rather not say/Don't know should be grey

@@

module2%>%
  filter(!row_number() %in% c(1,2)) %>% 
  select(starts_with("Ben"))%>%
  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDLPG, factor_key = TRUE)%>%
  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
  select(-Ben) %>%
  group_by(Technology, Perceived_Benefit) %>%
  summarise(n=n())%>%
ggplot(aes(fill= Perceived_Benefit, y=n, x=Technology)) + 
  geom_bar(position="fill", stat="identity")+
  coord_flip()

# fix ugly visual. Rearrange from extremely beneficial to not at all beneficial. Green to red, rather not say/Don't know should be grey. Also facet wrap by INDividually owned and centrally owned technology.
